---
title: "knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(knapsack)
set.seed(42)
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```



# 1.1.2 Brute force search

```{r}
a <- proc.time()
brute_result <- brute_force_knapsack_unopt(x=knapsack_objects[1:16,],W=3500)
b <- proc.time()
b-a
```

The brute force search takes `r (b-a)[3]` seconds to complete with 16 objects.

# 1.1.3 Dynamic programming

```{r}
a <- proc.time()
dynamic_result <- knapsack_dynamic(x=knapsack_objects[1:500,],W=3500)
b <- proc.time()
b-a
```

The dynamic programming search takes `r (b-a)[3]` seconds to complete with 500 objects.


# 1.1.4 Greedy heuristic

```{r}
set.seed(42)
n <- 1000000
knapsack_objects_2 <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```


```{r}
a <- proc.time()
greedy_result <- greedy_knapsack(x=knapsack_objects_2[1:1000000,], W=3500)
b <- proc.time()
b-a
```

The greedy heuristic search takes `r (b-a)[3]` seconds to complete with 1.000.000 objects.


# 1.1.6 Optimize your code

Using the profvis package to profile the code, it could be observed that for the brute force algorithm there was a section of the code which was significantly more time consuming:

```{r, eval= FALSE}
for (row in 1:n) {
      if(bitmat[row,col]==1){
        weights <- weights + x[row,1]
        values <- values + x[row,2]
        items <- c(items, row)
      }
    }
```

As there is an argument W for the maximum weight, one way to optimize this section was to add a check after the weights are updated to see if they are greater than W. In this case the loop can break without updating the values and the items and instead move on to the next combination of items. The optimized code section instead looks like:

```{r, eval=FALSE}
for (row in 1:n) {
      if(bitmat[row,col]==1){
        weights <- weights + x[row,1]
        if(weights > W){break}
        values <- values + x[row,2]
        items <- c(items, row)
      }
}
```

The optimized function can now be compared with the original function:

```{r}
a <- proc.time()
brute_result_2 <- brute_force_knapsack(x=knapsack_objects[1:16,],W=3500)
b <- proc.time()
b-a
```

The optimized brute force search takes `r (b-a)[3]` seconds to complete with 16 objects, which is much faster than before the code was optimized.


# 1.1.8 Parallelize brute force search

```{r}

```

